\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
highlight

\usepackage{multirow}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{enumitem}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\begin{lstlisting}[language=bash]
$> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
$> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash]
...  
[Reproducing the bug]
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
...
IndexError: list index out of range
====== 1 passed in 1.09s ======
...

[Setting up FreeFuzz]
Updating environment in the container of the testing tool
Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
__pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
...

[Running FreeFuzz]
Running the testing tool on the environment of the bug
Testing on  ['torch']
torch.log2
...
torch.nn.MaxUnpool2d
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
...
\end{lstlisting}

>>>>

\usepackage{multirow}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{enumitem}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
  escapeinside={(*@}{@*)},
}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\begin{lstlisting}[language=bash,keywords={}]
$> cd tool-integration/FreeFuzz && bash install_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
#!/bin/bash
git clone https://github.com/ise-uiuc/FreeFuzz.git
docker build -t freefuzz .
docker run --name freefuzz --gpus all -d freefuzz:latest
docker exec -it freefuzz mongorestore dump/
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
$> run-tool --container freefuzz --library-name pytorch --bug-id 117033 --run-script tool-integration/FreeFuzz/run_freefuzz_docker.sh
\end{lstlisting}

@@

\begin{lstlisting}[language=bash,keywords={}]
...  
(*@\textbf{[Reproducing the bug]}@*)
====== test session starts ======
platform linux -- Python 3.10.0, pytest-8.3.3, pluggy-1.5.0
...
IndexError: list index out of range
====== 1 passed in 1.09s ======
...

(*@\textbf{[Setting up FreeFuzz]}@*)
Updating environment in the container of the testing tool
Successfully copied 16.4kB to freefuzz:/tmp/issue_117033
__pycache__  install_environment.sh  reproduce_bug.sh  requirements.txt  test_issue_117033.py
...

(*@\textbf{[Running FreeFuzz]}@*)
Running the testing tool on the environment of the bug
Testing on  ['torch']
torch.log2
...
torch.nn.MaxUnpool2d
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [1,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
../aten/src/ATen/native/cuda/MaxUnpooling.cu:47: max_unpooling2d_forward_kernel: block: [0,0,0], thread: [2,0,0] Assertion `maxind >= 0 && maxind < outputImageSize` failed.
...
\end{lstlisting}
